\newpage

\section{Analytics}
\label{sec:Analytics}

\subsection{Linear approximation}
According to the model which was described in the section \ref{sec:Model} the equilibrium states of the magnetization vector in each sublattice directed along $z$ axis:
$$
	\mb{M}^0_k = \bra{0, 0, (-1)^{k+1}M_0}
$$
where $M_0$ -- saturation value of the magnetization.

Let's assume that the magnetization vector is slightly deviated from the equilibrium states by the value which is much smaller then $M_0$. This excited vector can be written as a sum of two perpendicular vectors:
$$
	\mb{M}_k = \mb{m}_k + \mb{M}_{kz},
$$
where $\mb{m}_k$ is a small vector which lies on $xy$ plane.

The equations of motion (\ref{eq:LLGS}) leave the magnitude of the magnetization vector constant, so $\abs{\mb{M}_k} = M_0$. In this case, the magnitude of the $\mb{M}_{kz}$ can be approximated as following:
\bea
	\mb{M}_{kz}			&=& \mb{M}_k - \mb{m}_k; 						\nn \\
	M_{kz}^2 			&=& M_k^2 - 2\mb{M}_k \cdot \mb{m}_k + m_k^2 	\nn \\
						&=& M_k^2 - m_k^2 = M_0^2 - m_k^2; 				\nn \\
	\abs{\mb{M}_{kz}} 	&=& \sqrt{M_0^2 - m_k^2} = M_0 \sqrt{1-\frac{m_k^2}{M_0^2}} \nn
\eea

The expending of the last expression in the Taylor series gives	$M_{kz} \approx M_0 \bra{1-\frac{1}{2}\frac{m_i^2}{M_0^2}}$. Hence, in linear approximation the magnetization vector can be considered as following:
\be
\label{eq:magn}
	\mb{M}_k = \bra{m_{kx}, m_{kx}, (-1)^{k+1}M_0}
\ee

In our case the current flowing through the bulk is a source of the external amount of energy which manifesting in the deviations of the magnetization vector from it equilibrium state. The internal damping dissipate this energy. So, there is a value of the current when this two processes compensate each other. This value is called critical current. Let's find it analytical expression.

By substituting the expression for magnetization vector (\ref{eq:magn}) into the equations of motion (\ref{eq:LLGS}) and neglecting the terms of the \emph{second order of smallness} (Here we assume that the small quantity is one of the vectors $\mb{m}_k$ or it component) we obtain a system of equations for deviation terms:
\bea
	\label{eq:analytical_study:momentum_motion}
	\dot{m}_{1x} &=&	- \sigma I							m_{1x}
						- \gamma M_0 ( J_\text{int} + K )	m_{1y}
						- \gamma M_0 J_\text{int}			m_{2y}
						- \alpha_G							\dot{m}_{1y}	\nn \\
	\dot{m}_{1y} &=&	  \gamma M_0 ( J_\text{int} + K )	m_{1x}
						- \sigma I							m_{1y}
						+ \gamma M_0 J_\text{int}			m_{2x}
						+ \alpha_G							\dot{m}_{1x}	\nn \\
	\dot{m}_{2x} &=&	  \gamma M_0 J_\text{int}			m_{1y}
						- \sigma I							m_{2x}
						+ \gamma M_0 ( J_\text{int} + K )	m_{2y}
						+ \alpha_G							\dot{m}_{2y}	\nn \\
	\dot{m}_{2y} &=&	- \gamma M_0 J_\text{int}			m_{1x}
						- \gamma M_0 ( J_\text{int} + K )	m_{2x}
						- \sigma I							m_{2y}
						- \alpha_G							\dot{m}_{2x}
\eea

The solutions of this system of equations we will seek in the exponent form $m_i \sim e^{i\omega t}$. In this case the eigenvalues of the frequency is following:
\bea
	\label{eq:analytical_study:dissipative_frequency}
	\omega &=&	i \frac{ \sigma I + \gamma M_0 (K + J_\text{int}) \alpha_G }{\alpha_G^2 + 1} \\
				&\pm& \frac{\sqrt{ (\gamma M_0 (K + J_\text{int}) - \alpha_G \sigma I )^2 - (\gamma M_0 J_\text{int})^2( \alpha_G^2 + 1 )} }{ \alpha_G^2 + 1 } \nn
\eea

This expression is complex value.
The real part of it is responsible for the frequency of precession of magnetization vector around the preferred direction in the ferromagnetic layer. 
The imaginary part is responsible for either increasing or decreasing of the amplitude of precession. It is determined by the ratio between amount of pumping and damping energy.










